---
title: "Week4Homework"
output: html_document
---

This is my Week 4 homework assignment for CASA0005.

The task this week is to:

Read in global gender inequality data

Join the global gender inequality index to spatial data of the World, creating a new column of difference in inequality between 2010 and 2019

Share it with the World on GitHub

Add your repository URL to the circulated spreadsheet

# Load libraries and read data
```{r}
library(sf)
library(here)
library(countrycode)
library(dplyr)
library(tmap)
library(tmaptools)

gender<-read.csv(here::here('Gender Inequality Index (GII).csv'))
countries<-st_read(here::here('World_Countries__Generalized_.shp'))
```

# Create variable for 2010-2019 equality difference
```{r}
gender[gender=='..']<-NA

improve<-function(x,y,NA.RM=TRUE){
  x-y
}

gender$improvement<-improve(x=as.numeric(gender$X2010),y=as.numeric(gender$X2019))
```

The added 'improvement' variable in this data represents the change in gender inequality index for a given country between 2010 and 2019, where a negative score indicates a decrease in gender equality and a positive score indicates an increase in gender equality.

# Join CSV to spatial data
```{r}
gender2<-gender%>%
  slice(1:189,)%>%
  mutate(iso_code=countrycode(Country,origin ='country.name', destination = 'iso2c' ))

equality_shapefile<-left_join(countries,gender2,by=c('AFF_ISO'='iso_code'))
```

Below is a quick map illustrating the global change in gender equality between 2010 and 2019.

```{r}
tm_shape(equality_shapefile)+
  tm_polygons('improvement')
```












