---
title: "Week4Homework"
output: html_document
---

```{r}
install.packages(usethis)
library(usethis)

```


This is my Week 4 homework assignment for CASA0005.

The task this week is to:

Read in global gender inequality data

Join the global gender inequality index to spatial data of the World, creating a new column of difference in inequality between 2010 and 2019

Share it with the World on GitHub

Add you repository URL to the circulated spreadsheet

```{r}
library(sf)
gender<-read.csv('Gender Inequality Index (GII).csv')
countries<-st_read('World_Countries__Generalized_.shp')
```
```{r}
gender[gender=='..']<-NA

improve<-function(x,y,NA.RM=TRUE){
  x-y
}

gender$improvement<-improve(x=as.numeric(gender$X2010),y=as.numeric(gender$X2019))
```

The added 'improvement' variable in this data represents the change in gender inequality index for a given country between 2010 and 2019, where a negative score indicates a decrease in gender equality and a positive score indicates an increase in gender equality.

```{r}
equality_shapefile<-merge(countries,gender,by.x='COUNTRYAFF',by.y='Country')
```



